### 2019-08-29 Writeup/Thesis/chapters/lit_review.tex
Changes; - Fixed formatting issues

\newpage
\subsubsection*{Pretty Easy Privacy}
\label{sec:pep}
A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}. \pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS. The embedded design principles state that above all the systems should be easy to install, use and understand.

@@

\begin{wrapfigure}{l}{5cm}
    \centering
    \begin{BVerbatim}
    [...]
52127 ZYGOTE
52128 ZYGOTIC
52129 ZYMURGY
52130 AACHEN
52131 AARDVARK
52132 AAREN
    [...]
    \end{BVerbatim}
    \caption{Re-mapping position in Trustword dictionary}
    \label{fig:remap}
\end{wrapfigure}

@@

\begin{figure}[!h]
    \begin{center}
        \verb|TARGET: d6:b7:df:31:aa:55:d2:56:9b:32:71:61:24:08:44:87|
        \verb|MATCH:  d6:b7:8f:a6:fa:21:0c:0d:7d:0a:fb:9d:30:90:4a:87|
    \end{center}
    \caption{Best match obtained after a few minutes of hashing}
    \label{ref:fuzz}
\end{figure}

>>>>

\newpage
\subsubsection*{Pretty Easy Privacy}
\label{sec:pep}
A very recent implementation of a word list can be found in Pretty Easy Privacy (\pep) implementation of TrustWords\footnote{\url{https://tools.ietf.org/html/draft-birk-pep-trustwords-03}}. \pep is a data encryption system that utilises PGP encryption to provide E2EE on all common channels of communication such as email or SMS. The embedded design principles state that above all the systems should be easy to install, use and understand.

@@

\begin{wrapfigure}[11]{l}{5cm}
    \centering
    \begin{BVerbatim}
    [...]
52127 ZYGOTE
52128 ZYGOTIC
52129 ZYMURGY
52130 AACHEN
52131 AARDVARK
52132 AAREN
    [...]
    \end{BVerbatim}
    \caption{Re-mapping position}
    \label{fig:remap}
\end{wrapfigure}

@@

\begin{figure}[!h]
    \centering
    \verb|TARGET: d6:b7:df:31:aa:55:d2:56:9b:32:71:61:24:08:44:87|
    \verb|MATCH:  d6:b7:8f:a6:fa:21:0c:0d:7d:0a:fb:9d:30:90:4a:87|
    \caption{Best match obtained after a few minutes of hashing}
    \label{ref:fuzz}
\end{figure}
